Extending Morphological Chains with Supervised Learning and Cross-Language Features

### 2015-12-10 paper/paper.tex
paper

>>>>

\section{Experimental Validation}

\subsection{Data}

We used the datasets provided by 2010 Morpho Challenges. For English, this includes
a wordlist with word frequencies of approximately 878,000 words scraped from the
Wortschatz collection from the University of Leipzig, CLEF, and the Europarl corpus
as well as gold standard segmentation training and development sets of approximately 
1000 randomly selected words. Gold standard segmentation is based on the CELEX database.
For Turkish, the word list contains approximately
